Pulling oral and IV data from CvTdb

### 2025-08-05 data-raw/pulling_oral_iv_data_cvtdb.Rmd
Update to cvt fitting options and tkstats + parameter table generation for dashboard.

my_pk <- my_pk +
  stat_error_model(Chemical, Species) +
  settings_optimx(method = "bobyqa") +
  facet_data(Chemical, Species) +
  settings_preprocess(
    keep_data_original = TRUE,
    suppress.messages = TRUE
  ) +
  scale_conc(dose_norm = TRUE, log10_trans = TRUE)

@@

mirai::daemons(8)
mirai::everywhere(devtools::load_all())
my_pk <- do_fit(my_pk, async = TRUE)
mirai::daemons(0)

@@

write_csv(
  eval_tkstats(my_pk),
  file = paste0(
    Sys.getenv("FIG_DIR"),
    "2025_07_31_eval_tkstats.csv"
  )
)

>>>>

my_pk <- my_pk +
  stat_error_model(Chemical, Species) +
  settings_optimx(method = "bobyqa") +
  facet_data(Chemical, Species) +
  settings_preprocess(
    keep_data_original = TRUE,
    suppress.messages = TRUE
  ) +
  scale_conc(dose_norm = FALSE, log10_trans = FALSE)

@@

mirai::daemons(8L)
mirai::everywhere(devtools::load_all())
my_pk <- do_fit(my_pk, async = TRUE)
mirai::daemons(0L)

@@

my_tkstats <- eval_tkstats(my_pk, dose_norm = TRUE)
my_fit <- get_fit(my_pk)
my_wm <- get_winning_model(my_pk)

my_fit |>
  select(DATA_GROUP_ID:param_name, estimate) |>
  inner_join(my_wm, by = c("Chemical", "Species", "method", "model")) |>
  select(-c(near_flat, preds_below_loq)) |>
  filter(stringr::str_detect(param_name, "sigma_", negate = TRUE)) |>
  mutate(
    estimate = purrr::map_dbl(
      estimate,
      \(x) ifelse(is.null(x), NA_real_, as.numeric(x))
    )
  ) |> 
  tidyr::pivot_wider(names_from = param_name, values_from = estimate) |> 
  inner_join(my_tkstats,
             by = join_by(DATA_GROUP_ID, model, method, Chemical, Species)) |>
  readr::write_csv(
    file = paste0(
      Sys.getenv("FIG_DIR"),
      "20250805_pk000_evalTKstats.csv"
    )
  )
